I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-24 lipics-master/introduction.tex
intro

\item Our third main contribution is to experimentally confirm that focusing on compensations {\em does} improve accuracy: we introduce {\CMP} (Algorithm \ref{algo1}), building on our theoretical insights. This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones. Our extensive empirical evaluation (refer to Table \ref{tab:example}) reveals {\CMP} achieves a beneficial balance between accuracy and completeness compared to prevailing methods. It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$. Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete}) on the larger $6 \times 500$ DNN.

>>>>

\item Our third main contribution is to experimentally confirm that focusing on compensations {\em does} improve accuracy: we introduce {\CMP} (Algorithm \ref{algo1}), building on our theoretical insights. This method prioritizes ReLU nodes based on the weights of their associated compensating paths and differentiates their treatment in the MILP model, employing binary constraints for heavier nodes and linear constraints for lighter ones. Our empirical evaluation (refer to Table \ref{tab:example}) reveals {\CMP} achieves a beneficial balance between accuracy and completeness compared to prevailing methods. It reduces the proportion of undecided inputs from 17.6\% (as seen with $\beta$-Crown \cite{crown}) to 10.4\% on the DNN architecture of $8 \times 200$. Moreover, it verifies over 20\% more images than $\alpha,\beta$-CROWN \cite{xu2020fast} (or PRIMA \cite{prima}, MN-BaB \cite{ferrari2022complete}) on the larger $6 \times 500$ DNN.
